How young children integrate information sources to infer the meaning of words

### 2020-10-23 paper/supplementary_material.Rmd
prep for submission

---
title: "Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

@@

```{r fig2, include = T, fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition. B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution. Dots show individual datapoints. Lighter colors indicate later rated age of acquisition. Dotted line indicates a level of performance expected by chance. C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
```

>>>>

---
title: "How young children integrate information sources to infer the meaning of words"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

```{r}
#fig2 <- ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
#ggsave(plot = fig2, "../figures/figureS2.png", width = 12, height = 4)
```

@@

```{r fig2, include = T, fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition. B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution. Dots show individual datapoints. Lighter colors indicate later rated age of acquisition. Dotted line indicates a level of performance expected by chance. C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", out.width="100%"}
knitr::include_graphics("../figures/figureS2.png")
```
